\ttitle

### 2015-06-02 Chapters/Introduction.tex
Jaundice introduction - first sentence only
Committing to Jaundice branch

\section{The Jaundiced Patient}
\subsection{Impact of jaundice on cardiovascular physiology}
\subsection{Impact of jaundice on renal physiology}
\subsection{Impact of jaundice on the immune system}
\subsection{Jaundice and postoperative outcomes}
\subsection{Role of preoperative biliary drainage}

>>>>

\section{The Jaundiced Patient}
Obstructive jaundice is the most common presenting symptom in patients with pancreatic cancer involving the head of the pancreas and the periampullary region due to the anatomical location of the distal bile duct. Obstructive jaundice is known to have a wide range of effects on multiple organ systems including the cardiovascular system, immune system, coagulation cascade, as well as hepatic function.

\subsection{Impact of jaundice on cardiovascular physiology}
\subsection{Impact of jaundice on renal physiology}
\subsection{Impact of jaundice on the immune system}
\subsection{Jaundice and postoperative outcomes}
\subsection{Role of preoperative biliary drainage}
